---
title: "6 - Project Clones"
output: html_notebook
---

```{r setup, echo=F, results='hide'}
Sys.setenv(R_NOTEBOOK_HOME = getwd())
source("config.R")
source("helpers.R")
```

First, the input data for `clone_finder` must be exported:

```{r}
exportCloneFinderData(DATASET_NAME, DATASET_PATH)
```

Once done, you may run the `clone_finder NUM_THREADS FOLDER THRESHOLD`:

```{bash}
cd $R_NOTEBOOK_HOME
tools/clone_finder/build/clone_finder 1 datasets/js 2
```
     
Where `NUM_THREADS` is the number of threads the clone finder may use, `FOLDER` is the dataset folder and `THRESHOLD` is the minimal inclusive number of tokens the files must have to be considered. To proceed without modifications, set the number of threads to `1`. 

Then, load the data into database:

```{r}
importCloneFinderData(DATASET_NAME, DATASET_PATH, 1)
```

Where the last argument is number of threads the `clone_finder` used and must therefore be adjusted accordingly before running the script.

## Next Steps

[Metadata Acquisition](6-metadata.nb.html) in file [`6-metadata.Rmd`](6-metadata.Rmd).
