---
title: "9 - Language specific reporting"
output: html_notebook
---

```{r setup, echo=F, results='hide'}
library(ggplot2)
source("config.R")
source("helpers.R")
```

> This R notebook can be executed from within R, you can update the database connection properties and the dataset settings in the `config.R` file, or run the commands specified here interactively if you want to experiment. **Note that this notebook is only valid when javascript pipeline datasets are used.**

## Fig 6 - JavaScript files over time, with and without NPM files.

```{r}
js_aggregate = read.table(paste.path(DATASET_PATH,"aggregated_files.csv"), header = F, col.names = c("time", 1:32), colClasses = rep("integer", 33))
```

```{r}
filesOverTime(DATASET_NAME, js_aggregate, paste("time_",DATASET_NAME,"_files_bw.pdf", sep = ""))
nonNpmFilesOverTime(DATASET_NAME, js_aggregate, paste("time_",DATASET_NAME,"_files_nonpm_bw.pdf", sep = ""))
```



## Fig 7 -  Percentage of clones over time

```{r}
nonUniqueFilesOverTime(DATASET_NAME, js_aggregate, paste("time_", DATASET_NAME, "_dup_bw.pdf", sep = ""), bounds = c(0, 100))
```



## Fig 8 - % of NPM files in projects and directly imported NPM packages

```{r}
npmFilesInProjects(DATASET_NAME)
npmDirectImports(DATASET_NAME)
```

## Fig 9 - Popularity of NPM modules.

```{r}
npmPopularity(DATASET_NAME)
```

# NPM and non-NPM Versions of Common Graphs

## Figuree 3

```{r}
js_npm_cloneGroupSize(DATASET_NAME)
```


## Files per project 

```{r}
js_npm_filesPerProject(DATASET_NAME)
```

## SLOC per file

```{r}
js_npm_slocPerFile(DATASET_NAME)
```

## Stars per Project

```{r}
js_npm_starsPerProject(DATASET_NAME)
```


## Commits per project

```{r}
js_npm_commitsPerProject(DATASET_NAME)
```

## Qualitative Analysis

project with the most only npm files:


```{r}
sql.connect(dbname = "js")
```

```
SELECT js.projects.projectId, js.projects.files, js.projects.projectUrl FROM ( SELECT * FROM projects WHERE files = 0) AS X JOIN js.projects ON X.projectId = js.projects.projectId ORDER BY js.projects.files;
```

How many modules a project imports:

```
CREATE TABLE foo (SELECT MAX(npmDepth) AS maxDepth, COUNT(DISTINCT moduleName) AS modules, COUNT(DISTINCT blameModule) AS directModules, projectId FROM files_nm JOIN files ON files_nm.fileId = files.fileId GROUP BY projectId);
```

```{r}
summary(sql.query("SELECT maxDepth FROM foo WHERE maxDepth > 0")[[1]])
```

```{r}
summary(sql.query("SELECT modules FROM foo WHERE maxDepth > 0")[[1]])
```

To determine the most popular modules (blame modules), run the following SQL:

```
SELECT COUNT(DISTINCT projectId) as projects, blameModule FROM files_nm JOIN files ON files_nm.fileId = files.fileId GROUP BY blameModule ORDER BY projects DESC LIMIT 10;
```

To see how many projects have NPM files in them:

```
SELECT COUNT(DISTINCT projectId) FROM files WHERE npm != 0;
```

To determine most cloned projects:

```
java SccPreprocessor cstats PATH_TO_DATASET NUM_CHUNKS

CREATE TABLE fully_cloned_projects(
    projectId BIGINT NOT NULL,
    clones INT NOT NULL,
    PRIMARY KEY(projectId));
LOAD DATA INFILE '/home/peta/datasets/js/fully_cloned_projects2.csv' INTO TABLE fully_cloned_projects FIELDS TERMINATED BY ',' LINES TERMINATED BY '\n';

SELECT projectUrl, clones FROM fully_cloned_projects JOIN projects ON fully_cloned_projects.projectId = projects.projectId ORDER BY clones DESC LIMIT 40;
```

To determine which files are cloned the most:

```
SELECT COUNT(*) AS cnt FROM files GROUP BY fileHash ORDER BY cnt DESC LIMIT 20;
```



```
SELECT COUNT(DISTINCT fileHash) AS distinct, COUNT(*) AS count FROM files WHERE projectId IN SELECT projectId FROM projects ORDER BY commits DESC LIMIT 10000 AS x;

```
